### 2018-04-19 paper/algorithm.tex
Introduces some subsections in algorithm section

\NewScheme{\SPOR}{SPOR}
\NewAlgorithm{\Send}{Send}
\NewAlgorithm{\Fwd}{Forward}
\NewAlgorithm{\Recv}{Receive}
\NewVariable{\rdv}{rdv}

@@

\commentDaniel{Anything below this line should be updated.}

A set of users $\mathcal{U}$ participate in the \name network.
Each user $u \in \mathcal{U}$ has a set $\mathcal{D}_u$ of devices that contribute to the system when online.
Alice and Bob use \name to exchange a file secretly: no participant will learn who sends and receives it, nor its content.

>>>>

\NewScheme{\SPOR}{SPOR}

\subsection{\(\SPOR\)}

\NewAlgorithm{\Send}{Send}
\NewAlgorithm{\Fwd}{Forward}
\NewAlgorithm{\Recv}{Receive}
\NewVariable{\rdv}{rdv}

@@

\subsection{Predictions and scheduling}

\commentDaniel{%
  We must cover how to do \(\Pr[d \text{ offline at time } t]\) as used above 
  (\cref{ExtendRoute}).%
}

\commentDaniel{%
  We must do the scheduling: \ie divide the file \(f\) into \(f_1, \dotsc, f_n\) 
  and how the size of \(f_i\) relates to transmission time and size of the 
  timeslot (for the validity of predictions).
  After that we just do \(\SPOR[\Send]\) on each \(f_i\).%
}

\subsection{Adrien's old stuff}

\commentDaniel{%
  Anything below this line should be updated, integrated or removed.%
}
A set of users $\mathcal{U}$ participate in the \name network.
Each user $u \in \mathcal{U}$ has a set $\mathcal{D}_u$ of devices that contribute to the system when online.
Alice and Bob use \name to exchange a file secretly: no participant will learn who sends and receives it, nor its content.
